Embedding intuitionistic into classical logic

### 2022-07-07 Notes/Embedding intuitionistic into classical logic/EIICL.tex
CLS paper

\usepackage{amsmath,amssymb,amsthm}
\usepackage{ wasysym }
\usepackage{ stmaryrd }
\usepackage{ mathpartir }
\usepackage{bussproofs}
\usepackage{enumerate}
\usepackage{tikz-qtree}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows.meta}
\usepackage{stackengine}
\usepackage{bbold}
\usepackage{footmisc}

@@

	\begin{definition}
		A $\Sigma$-\textit{Kripke structure} $\mathcal{K}$ is a partially ordered set $W$ and a family of $\Sigma$-structures $(\mathcal{M}_w)_{w\in W}$ such that for $u\leq w$
		\begin{itemize}
			\item $M_u\subseteq M_w$.
			\item $f^{I_w}|_{M_u} = f^{I_u}$.
			\item $R^{I_w}|_{M_u} = f^{I_u}$.
		\end{itemize}
		Then we define a model relation between worlds $u\in W$ and variable assignments $v$ (targeting $M_u$) and formulas $\varphi$ as follows:
		\begin{itemize}
			\item $u, v\not\models\bot$
			\item $u, v\models R(t_1,\dots,t_n)$ iff $(t_1^{I_u, v},\dots,t_n^{I_u, v})\in R^{I_u}$.
			\item $u, v\models s = t$ iff $s^{I_u, v} = t^{I_u, v}$.
			\item $u, v\models \varphi\wedge \psi$ iff $u, v\models\varphi$ and $u, v\models\psi$.
			\item $u, v\models \varphi\vee\psi$ iff $u, v\models\varphi$ or $u, v\models\psi$.
			\item $u, v\models \varphi\to\psi$ iff for every $w\geq u$ we have $w, v\not\models\varphi$ or $w, v\models\psi$.
			\item $u, v\models\exists x\varphi$ iff there exists $m\in M_u$ such that $u, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
			\item $u, v\models\forall x\varphi$ iff for every $w\geq u$ and $m\in M_w$ we have $w, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\end{itemize}
		We say that $\mathcal{K}$ satisfies $\varphi$ if $u, v\models\varphi$ holds for every world $u$ and variable assignment $v$. As always a formula is satisfiable if it is satisfies by some Kripke structure and it is valid if it is satisfied in every Kripke structure. We denote the set of valid formulas with IQC.  As before define an entailment relation $\models_I$ between sets of formulas.
	\end{definition}
	In addition to the propositional tautologies there are now sentences involving quantifiers which are classically valid but not intuitionistically.
	Consider for instance the classical tautology $\varphi$ $$\neg\forall x A(x)\to \exists x \neg A(x)$$We exhibit an intuitionistic counter model. Consider the Kripke structure with two nodes $u\leq w$ with $M_u = \{0\}, M_w = \{0, 1\}$ and $A^{I_u} = A^{I_w} = \{0\}$. Then $u, v\not\models \varphi$: First note that $w, v\not\models\forall xA(x)$ and $u, v\not\models\forall xA(x)$ for any valuation $v$ since $w, v[1, a]\not\models A(a)$, i.e. $u, v\models\neg\forall xA(x)$ and also $w, v\models\neg\forall xA(x)$. Furthermore $u, v[0/a]\not\models \neg A(a)$ and $w, v[0/a]\not\models \neg A(a)$ so $u, v\not\models \exists x\neg A(x)$ for any valuation $v$ (note however that this is not true at $w$!). Therefore $u, v\not\models\varphi$.

@@

	The most obvious approach to embedding intuitionistic into classical logic is to express intuitionistic semantics, i.e. Kripke frames, as a first order theory. For every atom $A$ consider a unary predicate $A$ of the same name where $A(u)$ expresses that $A$ is true at some world $u$. We can then naively encode formulas as follows:

	\begin{definition}
		Let $\varphi$ be a propositional formula. Define $\varphi^{k}$ inductively as follows:
		\begin{itemize}
			\item $A^{k} = A(k)$ for every atom $A$.
			\item $(\varphi\wedge\psi)^k = \varphi^k\wedge\psi^k$.
			\item $(\varphi\vee\psi)^k = \varphi^k\vee\psi^k$.
			\item $(\varphi\to \psi)^k = \forall u(k\preceq u\to\varphi^{u}\to\psi^{u})$ where $u$ is some new free variable.
		\end{itemize}
		Let $K(\varphi)$ encode that $\preceq$ is a partial order, the persistency condition for all propositional variables occurring in $\varphi$ and ex falso quodlibet for each world, i.e.
		\begin{align*}
			K(\varphi) = &\forall k(k\preceq k)\wedge \forall k\forall l(k\preceq l\to l\preceq k\to l = k) \wedge \\&\forall k\forall l\forall m(k\preceq l \to l\preceq m\to k\preceq m)\wedge\\&\bigwedge \{\forall k\forall l(k\preceq l\to A(k)\to A(l))\:|\: \text{ $A$ occurs in $\varphi$}\}\wedge\\&\bigwedge\{\forall k(\bot(k)\to A(k))\:|\: A \text{ occurs in }\varphi\}
		\end{align*}
		Then define
		$$\varphi^{C} = K(\varphi)\to \varphi^{u}$$
		where $u$ is some free variable.
	\end{definition}

	All that we have done is model Kripke frames with a finite number of propositional variables as a first-order theory. The only attention must be paid with regard to $\bot$, which we have encoded because it will be useful for translation to propositional logic later. Consider the formula $\varphi^C_\bot$, which is exactly as above except that $\bot^k = \bot$. If we have a counter model to $\varphi^C_\bot$ we obtain a counter model for $\varphi^C$ by setting $\bot(k)$ false for all $k$. On the other hand if we have a counter model for $\varphi^C$ then we obtain one for $\varphi^C_\bot$ by restricting our domain to all $u$ for which $\bot(u)$ does not hold. Therefore this modification is unproblematic and we have:

@@

	\begin{example}
		Consider the law of excluded middle $$\varphi = (A\to \bot)\vee A$$which is not intuitionistically valid. Then
		\begin{align*}
			\varphi^{C} &= K(\varphi)\to ((A\to \bot)\vee A)^u\\
						 &= K(\varphi)\to (A\to \bot)^u\vee A^u\\
						 &= K(\varphi)\to (\forall u'( u\preceq u' \to A^{u'}\to \bot^{u'})\vee A^\#(u))\\
						 &= K(\varphi)\to (\forall u' (u\preceq u' \to A(u')\to \bot(u'))\vee A(u))
		\end{align*}
		and indeed $\varphi^{C}$ admits a counter model with domain $\{u, u'\}$ where $u \preceq u'$, $A(u) = \bot(u) = \bot(u') = 0, A(u') = 1$.
	\end{example}

@@

	\begin{corollary}
		In both intuitionistic and classical logic
		\begin{itemize}
			\item $\varphi$ is satisfiable iff $\mathcal \bigwedge S^+(\varphi)\wedge P_\varphi(\vec t_\varphi)$ is. 
			\item $\varphi$ is valid iff $\bigwedge\mathcal S^-(\varphi)\to P_\varphi(\vec t_\varphi)$ is.
		\end{itemize}
	\end{corollary}

@@

	where we can treat $A\to B$ as a special case $A\to (B\wedge B)$. We then apply the transformation to CQC, leading to a formula
	$$\varphi'' = K(\varphi')\to\bigwedge  \mathcal S\to P_\varphi(u)$$
	where $u$ is some new free variable and each $\psi\in\mathcal S$ is of one of the forms
	$$\hspace*{-2mm}\forall k(u\preceq k\to A(k)\to (B_\psi(k)\wedge C_\psi(k))), \forall k(u\preceq k\to (A_\psi(k)\wedge (B_\psi(k))\to C_\psi(k)))$$
	$$\hspace*{-2mm}\forall k(u\preceq k\to A(k)\to (B_\psi(k)\vee C_\psi(k))), \forall k(u\preceq k\to (A_\psi(k)\vee (B_\psi(k))\to C_\psi(k)))$$
	$$\forall k(u\preceq k\to (\forall l(k\preceq l \to A_\psi(l)\to B_\psi(l))\to C_\psi(k)))$$

	Applying Herbrandization we obtain a formula
	$$\varphi''' = K(\varphi')\to \bigwedge \mathcal S'\to P_\varphi(s)$$
	where $s$ is some new constant term and each $\psi\in\mathcal S'$ is of one of the forms
	$$\hspace*{-2mm}\forall k(s\preceq k\to A_\psi(k)\to (B_\psi(k)\wedge C_\psi(k))), \forall k(s\preceq k\to (A_\psi(k)\wedge (B_\psi(k))\to C_\psi(k)))$$
	$$\hspace*{-2mm}\forall k(s\preceq k\to A_\psi(k)\to (B_\psi(k)\vee C_\psi(k))), \forall k(s\preceq k\to (A_\psi(k)\vee (B_\psi(k))\to C_\psi(k)))$$
	$$\forall k(s\preceq k\to (k\preceq f_\psi(k) \to A_\psi(f_\psi(k))\to B_\psi(f_\psi(k)))\to C_\psi(k))$$
	and $f$ is a new function symbol for each introduced formula of that form. Now if $(M, I)$ is a counter-model then we have a counter-model $(M',I')$ where $$M' = \{m\in M|s\preceq m\}$$ and 
	$$f_\psi^{I'}(u) = \begin{cases}
		f^I_\psi(u)&\text{ iff $u\preceq f^{I}_\psi(u)$}\\
		u&\text{ else}
	\end{cases}$$ that is where $s$ is a least element and the $f_\psi$ increase their argument. Therefore instead of $\varphi'''$ we may consider a formula $$\varphi^\circ = \forall k(s\preceq k)\to \bigwedge\{\forall k(k\preceq f_\psi(k))\:|\:\psi\in\mathcal F_\to\}\to K(\varphi')\to \bigwedge \mathcal S^\circ\to P_\varphi(s)$$ where each formula $\psi\in\mathcal S^\circ$ is of one of the forms
	$$\forall k(A_\psi(k)\to (B_\psi(k)\wedge C_\psi(k))), \forall k((A_\psi(k)\wedge B_\psi(k))\to C_\psi(k))$$
	$$\forall k(A_\psi(k)\to (B_\psi(k)\vee C_\psi(k))), \forall k((A_\psi(k)\vee B_\psi(k))\to C_\psi(k))$$
	$$\forall k((A_\psi(f_\psi(k))\to B_\psi(f_\psi(k)))\to C_\psi(k))$$
	and $\mathcal F_\to$ denotes the set of formulas of the last kind.

@@

	\begin{definition}
		Suppose we are given a counter-model $(M, I)$ for $\varphi^\circ$. For $\psi\in\mathcal F_\to$ we say that is it \textit{fulfilled} at a world $u\in M$ iff $A_\psi^I(u)\to B_\psi^I(u)$ is false or $C_\psi^I(u)$ is true. For $\psi\in\mathcal F_\to$ define $$g_\psi : M\to M, u\mapsto\begin{cases}
			u&\text{ if $\psi$ is fulfilled in $u$}\\
			f^I_\psi(u)&\text{ else}		
		\end{cases}$$Define a $(M_T, I_T)$ as follows:
	\begin{itemize}
		\item $M_T$ is the set of sequences without repetition on $\mathcal F_\to$.
		\item Interpret $\preceq$ as the prefix-order.
		\item Have $$f_\psi^{I_T}(\psi_1\dots\psi_n) = \begin{cases}
			\psi_1\dots\psi_n&\text{if $\psi$ occurs in $\psi_1\dots\psi_n$}\\
			\psi_1\dots\psi_n\psi&\text{else}			
		\end{cases}$$
		\item For propositional variables $P$ have $$P^{I_T}(x_1\dots x_n) = P^I(g_{\psi_n}(\dots(g_{\psi_1}(s^I))\dots))$$
	\end{itemize}
	\end{definition}

	The following easy technical Lemma is quite useful.
	\begin{lemma}
		Let $(M, I)$ be a counter-model to $\mathcal \varphi^\circ$.
		\begin{enumerate}
			\item $\psi$ is fulfilled at $f_\psi^I(u)$ for all $u\in M, \psi\in\mathcal F_\to$.
			\item If $\psi$ is fulfilled at some $u\in M$ then $\psi$ is fulfilled at all $w\geq u$.
		\end{enumerate}

@@

	\begin{corollary}
		If $(M, I)$ is a counter-model to $\varphi^\circ$ then so is $(M_T, I_T)$.
	\end{corollary}

	The size of this model is $|\mathcal F_\to|!$ in the theoretical worst case. While this would already allow us to return to the propositional world we can do better than that. In fact we can merge all branches into a model of size $2^{|\mathcal F_\to|}$.

	\begin{definition}
		Suppose we are given a counter-example $(M_T, I_T)$ to $\varphi^\circ$ as above. Consider $(M_F, I_F)$ as follows:
		\begin{itemize}
			\item $M_F = 2^{F_\to}$, i.e. the set of subsets of $F_\to$.
			\item $\preceq$ is interpreted as the subset relation.
			\item $s^{I_M} = \emptyset$, $f_\psi^{I_F}(u) = u\cup\{\psi\}$.
			\item For every atom $P$ have $P^{I_F}(u)$ iff for every $w\in M_T$ where each $\psi\in u$ is fulfilled we have $$P^{I_T}(w)$$
		\end{itemize}
	\end{definition}

	Note that in this definition for the first time it is of crucial importance that we have also transformed $\bot$ into a unary predicate that we may set to true, as this could be forced in certain cases, in particular if there is no $w$ at which each $\psi\in u$ is fulfilled.

	Of course we have to prove that this model transformation is correct:

	\begin{definition}
		If $(M_T, I_T)$ is a counter-model for $\varphi^\circ$ then so is $(M_F, I_F)$.
	\end{definition}
	\begin{proof}
		We have to check that all 5 types of formulas are still satisfied. The proofs for the first 4 are very similar, so we shall just present one.

		Suppose $\chi$ is of  the form $\forall k(A_\chi(k)\to (B_\chi(k)\vee C_\chi(k))$. Let $u\subseteq \mathcal F_\to$.
	\end{proof}

	Therefore we know that $\varphi^\circ$ is valid iff it is valid for structures with domain $2^{F_\to}$, i.e. the power-set of $F_\to$, ordered by the subset relation and $s^I = \emptyset, f_\psi^I(x) = x\cup\{\psi\}$. Thus we can replace all $\forall$-quantifiers by enumerating all the ground terms and finally all distinct ground instances of relations by new propositional variables yielding a CPC formula. This gives us the following translation:

	\begin{definition}
		Suppose $\mathcal S$ is a set of formulas of the form
		$$A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C),(A\vee B)\to C, (A\to B)\to C$$
		Let $\mathcal F_\to$ be the set of formulas of the form $(A\to B)\to C$. For each atom $A$ occurring in $\mathcal S$ and $M\subseteq \mathcal F_\to$ consider a new atom $A^{M}$, which will correspond to $A^{I_F}(M)$ from the previous definition. Obtain $\mathcal S^\#$ by including the formulas
		\begin{itemize}
			\item $\bot^N\to A^N, A^N\to A^M$ for atoms $A$ occurring in $\mathcal S$ and $N\subseteq M\subseteq \mathcal F_\to$.
			\item $A^M\to (B^M\circ C^M)$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $M\subseteq \mathcal F_\to$.
			\item $(A^M\circ B^M)\to C^M$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $M\subseteq \mathcal F_\to$.
			\item $(A^{M\cup \{\psi\}}\to B^{M\cup \{\psi\}})\to C^M$ for $\psi = (A\to B)\to C\in\mathcal S$, $M\subseteq \mathcal F_\to$.
		\end{itemize}
	\end{definition}

@@

	 Fix some set $\mathcal S$ of formulas $\psi$ of the form $$\hspace*{-.7cm}A_\psi\to (B_\psi\wedge C_\psi), (A_\psi\wedge B_\psi)\to C_\psi, A_\psi\to (B_\psi\vee C_\psi), (A_\psi\vee B_\psi)\to C_\psi, (A_\psi\to B_\psi)\to C_\psi$$and a formula $$\varphi = \bigwedge \mathcal S\to P$$
	and denote with $\mathcal F_\to$ the set of formulas of the form $(A\to B)\to C$. We will now formulate a QBF that expresses that $\varphi$ has an intuitionistic counter-model. The idea how to get a linear-size formula is instead of expressing validity at every node of $\mathcal M_F$ - which was done in the CPC translation - we express that in each path in $\mathcal M_F$ from $\emptyset$ to $F_\to$ the worlds on the way satisfy all conditions for $\mathcal M_F$ being a counter-model. The universally quantified variables $F_\psi$ in the next definition will express which path is considered.

>>>>

\usepackage{amsmath,amssymb,amsthm}
\usepackage{ wasysym }
\usepackage{ stmaryrd }
\usepackage{ mathpartir }
\usepackage{bussproofs}
\usepackage{enumerate}
\usepackage{tikz-qtree}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{arrows,shapes,quotes}
\usepackage{stackengine}
\usepackage{bbold}
\usepackage{footmisc}

@@

	\begin{definition}
		A $\Sigma$-\textit{Kripke structure} $\mathcal{K}$ is a partially ordered set $W$ and a family of $\Sigma$-structures $(\mathcal{M}_w)_{w\in W}$ such that for $u\leq w$
		\begin{itemize}
			\item $M_u\subseteq M_w$.
			\item $f^{I_w}|_{M_u} = f^{I_u}$.
			\item $R^{I_w}|_{M_u} = R^{I_u}$.
		\end{itemize}
		Then we define a model relation between worlds $u\in W$ and variable assignments $v$ (targeting $M_u$) and formulas $\varphi$ as follows:
		\begin{itemize}
			\item $u, v\not\models\bot$
			\item $u, v\models R(t_1,\dots,t_n)$ iff $(t_1^{I_u, v},\dots,t_n^{I_u, v})\in R^{I_u}$.
			\item $u, v\models s = t$ iff $s^{I_u, v} = t^{I_u, v}$.
			\item $u, v\models \varphi\wedge \psi$ iff $u, v\models\varphi$ and $u, v\models\psi$.
			\item $u, v\models \varphi\vee\psi$ iff $u, v\models\varphi$ or $u, v\models\psi$.
			\item $u, v\models \varphi\to\psi$ iff for every $w\geq u$ we have $w, v\not\models\varphi$ or $w, v\models\psi$.
			\item $u, v\models\exists x\varphi$ iff there exists $m\in M_u$ such that $u, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
			\item $u, v\models\forall x\varphi$ iff for every $w\geq u$ and $m\in M_w$ we have $w, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\end{itemize}
		We say that $\mathcal{K}$ satisfies $\varphi$ if $u, v\models\varphi$ holds for every world $u$ and variable assignment $v$. As always a formula is satisfiable if it is satisfies by some Kripke structure and it is valid if it is satisfied in every Kripke structure. We denote the set of valid formulas with IQC.  As before define an entailment relation $\models_I$ between sets of formulas.
	\end{definition}
	In addition to the propositional tautologies there are now sentences involving quantifiers which are classically valid but not intuitionistically.
	Consider for instance the classical tautology $\varphi$ $$\neg\forall x A(x)\to \exists x \neg A(x)$$We exhibit an intuitionistic counter model. Consider the Kripke structure with two nodes $u\leq w$ with $M_u = \{0\}, M_w = \{0, 1\}$ and $A^{I_u} = A^{I_w} = \{0\}$. Then $u, v\not\models \varphi$: First note that $w, v\not\models\forall xA(x)$ and $u, v\not\models\forall xA(x)$ for any valuation $v$ since $w, v[1, a]\not\models A(a)$, i.e. $u, v\models\neg\forall xA(x)$ and also $w, v\models\neg\forall xA(x)$. Furthermore $u, v[0/a]\not\models \neg A(a)$ and $w, v[0/a]\not\models \neg A(a)$ so $u, v\not\models \exists x\neg A(x)$ for any valuation $v$ (note however that this is not true at $w$!). Therefore $u, v\not\models\varphi$.

@@

	The most obvious approach to embedding intuitionistic into classical logic is to express intuitionistic semantics, i.e. Kripke frames, as a first order theory. For every propositional variable $A$ consider a unary predicate $A$ of the same name where $A(u)$ expresses that $A$ is true at some world $u$. We can then naively encode formulas as follows:

	\begin{definition}
		Let $\varphi$ be a propositional formula. Define $\varphi^{k}$ inductively as follows:
		\begin{itemize}
			\item $A^{k} = A(k)$ for every propositional variable $A$.
			\item $(\varphi\wedge\psi)^k = \varphi^k\wedge\psi^k$.
			\item $(\varphi\vee\psi)^k = \varphi^k\vee\psi^k$.
			\item $(\varphi\to \psi)^k = \forall u(k\preceq u\to\varphi^{u}\to\psi^{u})$ where $u$ is some new free variable.
		\end{itemize}
		Let $K(\varphi)$ encode that $\preceq$ is a partial order, the persistency condition for all propositional variables occurring in $\varphi$
		\begin{align*}
			K(\varphi) = &\forall k(k\preceq k)\wedge \forall k\forall l(k\preceq l\to l\preceq k\to l = k) \wedge \\&\forall k\forall l\forall m(k\preceq l \to l\preceq m\to k\preceq m)\wedge\\&\bigwedge \{\forall k\forall l(k\preceq l\to A(k)\to A(l))\:|\: \text{ $A$ occurs in $\varphi$}\}
		\end{align*}
		Then define
		$$\varphi^{C} = K(\varphi)\to \varphi^{u}$$
		where $u$ is some free variable.
	\end{definition}

	All that we have done is model Kripke frames with a finite number of propositional variables as a first-order theory and by definition we have

@@

	\begin{example}
		Consider the law of excluded middle $$\varphi = (A\to \bot)\vee A$$ which is not intuitionistically valid. Then
		\begin{align*}
			\varphi^{C} &= K(\varphi)\to ((A\to \bot)\vee A)^u\\
						 &= K(\varphi)\to (A\to \bot)^u\vee A^u\\
						 &= K(\varphi)\to (\forall u'( u\preceq u' \to A^{u'}\to \bot^{u'})\vee A(u))\\
						 &= K(\varphi)\to (\forall u' (u\preceq u' \to A(u')\to \bot(u'))\vee A(u))
		\end{align*}
		and indeed $\varphi^{C}$ admits a counter model with domain $\{u, u'\}$ where $u \preceq u'$, $A(u) = 0, A(u') = 1$.
	\end{example}

@@

	\begin{corollary}\label{equivalid}
		In both intuitionistic and classical logic
		\begin{itemize}
			\item $\varphi$ is satisfiable iff $\mathcal \bigwedge S^+(\varphi)\wedge P_\varphi(\vec t_\varphi)$ is. 
			\item $\varphi$ is valid iff $\bigwedge\mathcal S^-(\varphi)\to P_\varphi(\vec t_\varphi)$ is.
		\end{itemize}
	\end{corollary}

@@

	where we can treat $A\to B$ as a special case $A\to (B\wedge B)$. We then apply the transformation to CQC, leading to a formula
	$$\varphi'' = K(\varphi')\to\bigwedge  \mathcal S\to P_\varphi(u)$$
	where $u$ is some new free variable and each $\psi\in\mathcal S$ is of one of the forms
	$$\hspace*{-2mm}\forall k(u\preceq k\to A(k)\to (B_\psi(k)\wedge C_\psi(k))), \forall k(u\preceq k\to (A_\psi(k)\wedge (B_\psi(k))\to C_\psi(k)))$$
	$$\hspace*{-2mm}\forall k(u\preceq k\to A(k)\to (B_\psi(k)\vee C_\psi(k))), \forall k(u\preceq k\to (A_\psi(k)\vee B_\psi(k))\to C_\psi(k))$$
	$$\forall k(u\preceq k\to (\forall l(k\preceq l \to A_\psi(l)\to B_\psi(l))\to C_\psi(k)))$$
	with each $P(x)$ possibly being $\bot$. Applying Herbrandization we obtain a formula
	$$\varphi''' = K(\varphi')\to \bigwedge \mathcal S'\to P_\varphi(s)$$
	where $s$ is some new constant term and each $\psi\in\mathcal S'$ is of one of the forms
	$$\hspace*{-2mm}\forall k(s\preceq k\to A_\psi(k)\to (B_\psi(k)\wedge C_\psi(k))), \forall k(s\preceq k\to (A_\psi(k)\wedge (B_\psi(k))\to C_\psi(k)))$$
	$$\hspace*{-2mm}\forall k(s\preceq k\to A_\psi(k)\to (B_\psi(k)\vee C_\psi(k))), \forall k(s\preceq k\to (A_\psi(k)\vee (B_\psi(k))\to C_\psi(k)))$$
	$$\forall k(s\preceq k\to (k\preceq f_\psi(k) \to A_\psi(f_\psi(k))\to B_\psi(f_\psi(k)))\to C_\psi(k))$$
	and $f$ is a new function symbol for each introduced formula of that form. Now if $(M, I)$ is a counter-model then we have a counter-model $(M',I')$ where $$M' = \{m\in M|s\preceq m\}$$ and 
	$$f_\psi^{I'}(u) = \begin{cases}
		f^I_\psi(u)&\text{ iff $u\preceq f^{I}_\psi(u)$}\\
		u&\text{ else}
	\end{cases}$$ that is where $s$ is a least element and the $f_\psi$ increase their argument. Therefore instead of $\varphi'''$ we may consider a formula $$\varphi^\circ = \forall k(s\preceq k)\to \bigwedge\{\forall k(k\preceq f_\psi(k))\:|\:\psi\in\mathcal F_\to\}\to K(\varphi')\to \bigwedge \mathcal S^\circ\to P_\varphi(s)$$ where each formula $\psi\in\mathcal S^\circ$ is of one of the forms
	$$\forall k(A_\psi(k)\to (B_\psi(k)\wedge C_\psi(k))), \forall k((A_\psi(k)\wedge B_\psi(k))\to C_\psi(k))$$
	$$\forall k(A_\psi(k)\to (B_\psi(k)\vee C_\psi(k))), \forall k((A_\psi(k)\vee B_\psi(k))\to C_\psi(k))$$
	$$\forall k((A_\psi(f_\psi(k))\to B_\psi(f_\psi(k)))\to C_\psi(k))$$
	and $\mathcal F_\to$ denotes the set of formulas of the last kind.

@@

	\begin{definition}
		Suppose we are given a counter-model $\mathcal M = (M, I)$ for $\varphi^\circ$. For $\psi\in\mathcal F_\to$ we say that is it \textit{fulfilled} at $u\in M$ iff $A_\psi^I(u)\to B_\psi^I(u)$ is false or $C_\psi^I(u)$ is true. For $\psi\in\mathcal F_\to$ define $$g_\psi : M\to M, u\mapsto\begin{cases}
			u&\text{ if $\psi$ is fulfilled in $u$}\\
			f^I_\psi(u)&\text{ else}		
		\end{cases}$$Define a $\mathcal M_T = (M_T, I_T)$ as follows:
	\begin{itemize}
		\item $M_T$ is the set of sequences without repetition on $\mathcal F_\to$.
		\item Interpret $\preceq$ as the prefix-order.
		\item Have $$f_\psi^{I_T}(\psi_1\dots\psi_n) = \begin{cases}
			\psi_1\dots\psi_n&\text{if $\psi$ occurs in $\psi_1\dots\psi_n$}\\
			\psi_1\dots\psi_n\psi&\text{else}			
		\end{cases}$$
		\item For propositional variables $P$ have $$P^{I_T}(\psi_1\dots \psi_n) = P^I(g_{\psi_n}(\dots(g_{\psi_1}(s^I))\dots))$$
	\end{itemize}
	\end{definition}
	\begin{lemma}
		Let $\mathcal M = (M, I)$ be a counter-model to $\mathcal \varphi^\circ$.
		\begin{enumerate}
			\item $\psi$ is fulfilled at $f_\psi^I(u)$ for all $u\in M, \psi\in\mathcal F_\to$.
			\item If $\psi$ is fulfilled at some $u\in M$ then $\psi$ is fulfilled at all $w\geq u$.
		\end{enumerate}

@@

	\begin{corollary}
		If $\mathcal M$ is a counter-model to $\varphi^\circ$ then so is $\mathcal M_T$.
	\end{corollary}

	\begin{example}
		Consider
		$$\mathcal S = \{(A\to B)\to C, (B\to A)\to D, (A\wedge B)\to \bot, (C\vee D)\to E\}$$and $\varphi = \bigwedge S\to E$ which has the Kripke counter-model
		\begin{center}
			\begin{tikzpicture}[squarednode/.style={rectangle, draw, very thick, minimum size=5mm}]
				\node (center) {};
				\node[squarednode]      (right)   [right=of center] {$B, C$};
				\node[squarednode]      (left)    [left=of center] {$A, D$};
				\node[squarednode]      (lower)       	[below=of center] {};
				\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north west) -- (left.south east);
				\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north east) -- (right.south west);			
			\end{tikzpicture}
		\end{center}
		\vspace*{-.3cm}where at each node the true propositions are indicated.\pagebreak

		There is a corresponding classical counter-model $\mathcal M = (M, I)$ to $\varphi^\circ$ with $M = \{u, u_l, u_r\}$, $A^{I}(l) = D^I(l) = B^I(r) = C^I(r) = 1$ and $0$ else.

		 Denoting $\psi_1 := (A\to B)\to C$ and $\psi_2 := (A\to B)\to C$ this corresponds to a counter-model $\mathcal M_T = (M_T, I_T)$ of $\varphi^\circ$ with $M_T = \{\epsilon, \psi_1, \psi_2, \psi_1\psi_2, \psi_2\psi_1\}$ and interpretation as presented below
		\begin{center}
			\begin{tikzpicture}[squarednode/.style={rectangle, draw, very thick, minimum size=5mm}]
				\node (center) {};
				\node[squarednode]      (right1)   [right=of center] {$B, C$};
				\node[squarednode]      (right2)   [above=of right1] {$B, C$};
				\node[squarednode]      (left1)    [left=of center] {$A, D$};
				\node[squarednode]      (left2)    [above=of left1] {$A, D$};
				\node[squarednode]      (lower)       	[below=of center] {};
				\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north west) -- (left1.south east) node [midway, below left] {$f_{\psi_1}$};
				\draw[-{Stealth[length=3mm, width=3mm]}] (lower.north east) -- (right1.south west) node [midway, below right] {$f_{\psi_2}$};
				\draw[-{Stealth[length=3mm, width=3mm]}] (left1.north) -- (left2.south) node [midway, right] {$f_{\psi_2}$};
				\draw[-{Stealth[length=3mm, width=3mm]}] (right1.north) -- (right2.south) node [midway, left] {$f_{\psi_1}$};
				\draw[-{Stealth[length=3mm, width=3mm]}] (left1.south west) to [out=225, in=135, loop, looseness=3] node [left] {$f_{\psi_1}$} (left1.north west);		
				\draw[-{Stealth[length=3mm, width=3mm]}] (right1.south east) to [out=315, in=45, loop, looseness=3] node [right] {$f_{\psi_2}$} (right1.north east);
				\draw[-{Stealth[length=3mm, width=3mm]}] (left2.north west) to [out=135, in=45, loop, looseness=3] node [midway, above] {$f_{\psi_1}, f_{\psi_2}$} (left2.north east);
				\draw[-{Stealth[length=3mm, width=3mm]}] (right2.north west) to [out=135, in=45, loop, looseness=3] node [midway, above] {$f_{\psi_1}, f_{\psi_2}$} (right2.north east);		
			\end{tikzpicture}
		\end{center}
	\end{example}

	So we know that $\varphi^\circ$ is valid iff it is valid for structures that have as a domain the sequences without repetition over $\mathcal F_\to$, ordered by the prefix-relation and $$s^I = \epsilon, f_\psi^I(x) = \begin{cases}
		x&\text{ if $\psi$ occurs in $x$}\\
		x\psi&\text{ otherwise}
	\end{cases}$$ Now we can replace all $\forall$-quantifiers by enumerating all the ground terms and finally all distinct ground instances of relations by new propositional variables yielding a CPC formula. This gives us the following translation:

	\begin{definition}
		Suppose $\mathcal S$ is a set of formulas of the form
		$$A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C),(A\vee B)\to C, (A\to B)\to C$$
		Let $\mathcal F_\to$ be the set of formulas of the form $(A\to B)\to C$ and $\Lambda$ the set of sequences without repetition over $\mathcal F_\to$. For each atom $A$ occurring in $\mathcal S$ and $k\in \mathcal F_\to$ consider a new atom $A^{k}$, which will correspond to $A^{I_F}(k)$ from the previous definition. Obtain $\mathcal S^\#$ by including the formulas
		\begin{itemize}
			\item $A^k\to A^{k\psi}$ for $A$ occurring in $\mathcal S$, $k\in\Lambda$ and $\psi\in\mathcal F_\to$ not occurring in $k$.
			\item $A^k\to (B^k\circ C^k)$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
			\item $(A^k\circ B^k)\to C^k$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
			\item $(A^{k\psi}\to B^{k\psi})\to C^k$ for $\psi = (A\to B)\to C\in\mathcal S$, $k\in\Lambda$ if $\psi$ does not occurr in $k$.
		\end{itemize}
	\end{definition}

@@

	 Fix some set $\mathcal S$ of formulas $\psi$ of the form $$\hspace*{-.7cm}A_\psi\to (B_\psi\wedge C_\psi), (A_\psi\wedge B_\psi)\to C_\psi, A_\psi\to (B_\psi\vee C_\psi), (A_\psi\vee B_\psi)\to C_\psi, (A_\psi\to B_\psi)\to C_\psi$$and a formula $$\varphi = \bigwedge \mathcal S\to P$$
	and denote with $\mathcal F_\to$ the set of formulas of the form $(A\to B)\to C$. We will now formulate a QBF that expresses that $\varphi$ has an intuitionistic counter-model. The idea how to get a linear-size formula is: Instead of expressing validity at every node of $\mathcal M_T$ - which was done in the CPC translation - we express that on each path in $\mathcal M_T$ the nodes satisfy all conditions for $\mathcal M_T$ being a counter-model. The universally quantified variables $F_\psi$ in the next definition handle the branching, i.e. express which path is considered.
